\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{one}Popescu, A.M., Etzioni, O. and Kautz, H., 2003, January. Towards a theory of natural language interfaces to databases. In Proceedings of the 8th international conference on Intelligent user interfaces (pp. 149-157). ACM.

\bibitem{two}Androutsopoulos, I., Ritchie, G.D. and Thanisch, P., 1995. Natural language interfaces to databases–an introduction. Natural language engineering, 1(01), pp.29-81.

\bibitem{five} Rangel, R., Joaquín Pérez, O., Juan Javier González, B., Gelbukh, A., Sidorov, G. and Rodríguez, M., 2005. A domain independent natural language interface to databases capable of processing complex queries. MICAI 2005: Advances in Artificial Intelligence, pp.833-842.

\bibitem{six} González, B.J.J., Rangel, R.A.P., Fraire, H.H.J., de Santos Aguilar, L. and Pérez, O.J., 2006, November. Issues in translating from natural language to SQL in a domain-independent natural language interface to databases. In Mexican International Conference on Artificial Intelligence (pp. 922-931). Springer Berlin Heidelberg.

\bibitem{four} Stratica, N., Kosseim, L. and Desai, B.C., 2003, June. NLIDB Templates for Semantic Parsing. In NLDB (pp. 235-241).

\bibitem{eight} Nihalani, M.N., Silakari, S. and Motwani, M., 2011. Natural language interface for database: A brief review.

\bibitem{nine} Battan, A. and Chaudhary, A., 2014. Natural Language Interface to Databases-An Implementation. International Journal of Advanced Research in Computer Science, 5(6).

\bibitem{aaa} George A. Miller (1995). WordNet: A Lexical Database for English.
Communications of the ACM Vol. 38, No. 11: 39-41. \url{https://wordnet.princeton.edu/}

\bibitem{ten} M.-C. de Marne↵e, B. MacCartney, and C. D.
Manning. Generating typed dependency parses from
phrase structure parses. In LREC, pages 449–454,
2006

\bibitem{eleven} An SQL grammar  \url{http://www.mathcs.emory.edu/~cheung/Courses/554/Syllabus/5-query-opt/SQL-grammar.html}

\bibitem{tree} Y. Zeng, Z. Bao, T. W. Ling, H. V. Jagadish, and
G. Li. Breaking out of the mismatch trap. In ICDE,
pages 940–951, 2014.




\end{thebibliography}
